Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-23 Arxiv/main.tex
update
update the figure size

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_efficiency}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
\label{fig_theory}
\end{center}
\end{figure}
In Fig. \ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms. We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.4\textwidth]{sampling_3d.eps}   
\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_3d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.4\textwidth]{sampling_4d.eps}    
\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_4d}
\end{center}
\end{figure}

@@

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 50 to 100]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 100 to 200]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  % \subfigure[data size range from 200 to 500]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  % \subfigure[data size range from 500 to 1000]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}

>>>>

% \author[*]{Jiawen Liu}
% \author[**]{Mark Bun}
% \author[*]{Gian Pietro Farina}
% \author[*]{Marco Gaboardi}
% \affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
% \affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_efficiency}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.4\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.4\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
\label{fig_theory}
\end{center}
\end{figure}
In Fig. \ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms. We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.8\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
{
        \includegraphics[width=0.45\textwidth]{sampling_3d.eps} 
        \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$]
{
     \includegraphics[width=0.45\textwidth]{sampling_4d.eps} 
\label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

% \begin{figure}[ht]
% \begin{center}
% \centering

% \end{center}
% \end{figure}

@@

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 50 to 100]{
    \includegraphics[width=0.4\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 100 to 200]{
    \includegraphics[width=0.4\textwidth]{global_epsilon_size100to200.eps}} 
  % \subfigure[data size range from 200 to 500]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  % \subfigure[data size range from 500 to 1000]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}
